\documentclass{article}

\title{Assignment No. 2}
\author{Hamza Shahid (P200117), SE-7A}
\date{October 2023}

\begin{document}

\maketitle

\section{Company Information}
\subsection{Incorporation Name}
Honda Motor Company, Ltd

\subsection{Registered Office}
1-Mc Leod Road, Lahore-54000, Pakistan

\subsection{Incorporation Date}
Atlas Honda Limited is a public listed company incorporated on October 16, 1962.

\section{Financial Information}
\subsection{Type of Liability}
The company has current liabilities.

\subsection{Starting Share Capital}
\begin{itemize}
  \item Total Number of Shares: 42,000,000
  \item Cost per Share: Rs. 10
  \item Total Capital: Rs. 4200,000
\end{itemize}

\subsection{Current Share Capital}
\begin{itemize}
  \item Total Number of Shares: 17,100
  \item Cost per Share: Rs. 258.01 to Rs. 284
  \item Total Capital: Rs. 35.24 billion
\end{itemize}

\section{Directors' Terms}
Presently, the Board comprises of eight Directors, including three non-executive Directors, three executive Directors and two independent Directors. Non-executive Directors are elected to enhance objectivity. The existing board members were appointed by the shareholders in the Extraordinary General Meeting (EOGM) of the members of the Company, held on Monday, 13 March, 2023. These existing board was elected for a period of three years commencing from 14 March, 2023, in accordance with the provisions of section 159 of the Companies Act, 2017.

The Chairman of the Board of Directors is selected from within the Board. The statute requires the Board to formulate Audit Committee and Human Resource and Remuneration Committee. Additionally, the Board may from time to time establish committees, to assist it by focusing on specific responsibilities in greater detail than is possible for the Board as a whole, reporting to the Board and making any necessary recommendations.

AHL is an equal opportunity employer and members of the board are selected based on merit. AHL has not introduced any specific quotas for specific nationalities, ethnic minorities, or special age groups for the Board. AHL has, on its Board, highly competent and committed personnel with vast experience, expertise, integrity, and a strong sense of responsibility required for safeguarding stakeholders’ interests. The Board is comprised of qualified directors with diverse backgrounds in the field of business, finance, economics, engineering, and other disciplines. The Chairman is responsible for the overall discharge of the Board’s duties. The office of the Chairman and the Chief Executive Officer (CEO) are separate, and the Chairman is a non-executive Director,

All the matters including election, appointment and disclosure of interest are governed by the statutory requirements and regulations laid down by SECP and PSX. There were no non-compliances identified during the year. Further details about the Directors and matters carried out during the year can be found in the Director’s Profile and Statement of Compliance with the Code of Corporate Governance on page 26-27 and 128-129 respectively.

\end{document}

